Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/intro.tex

Standard approaches based on estimation of state-action
value functions, such as
\emph{Deep $Q$-learning} (DQN,~\citealt{dqn}) and \emph{Deep deterministic policy
gradient} (DDPG,~\citealt{ddpg}) are not at all \TODO{Remove familiar?
NDY it's not particularly familiar}robust to changes in time discretization. This is shown experimentally in Sec.~\ref{sec:exp}. 
Intuitively, as the discretization timestep
decreases, the effect of individual actions on the total return decreases
too: $Q^*(s,a)$ is the value of playing action $a$ then playing optimally,
and if $a$ is only maintained for a very short time its advantage over
other actions will be accordingly small. (This continuity effect occurs even with a
well-adjusted decay factor $\gamma$.) \TODO{Really relevant in the introduction?}

>>>>

Standard approaches based on estimation of state-action
value functions, such as
\emph{Deep $Q$-learning} (DQN,~\citealt{dqn}) and \emph{Deep deterministic policy
gradient} (DDPG,~\citealt{ddpg}) are not at all \TODO{Remove familiar?
NDY it's not particularly familiar}robust to changes in time discretization. This is shown experimentally in Sec.~\ref{sec:exp}. 
Intuitively, as the discretization timestep
decreases, the effect of individual actions on the total return decreases
too: $Q^*(s,a)$ is the value of playing action $a$ then playing optimally,
and if $a$ is only maintained for a very short time its advantage over
other actions will be accordingly small. (This continuity effect occurs even with a
well-adjusted decay factor $\gamma$.) \TODO{Really relevant in the
introduction? NDY Yes, I predict the first thing some people would say is
"you just put the wrong gamma, how stupid of you..."}
